A Dissection of Foregrounds in Epoch of Reionization Observations from the Murchison Widefield Array

### 2014-10-24 foreground_delay_spectrum_modeling.tex
Changed title

\shorttitle{Foreground signatures and mitigation in EoR H{\sc i} power spectra}
\shortauthors{Thyagarajan et~al.}

@@

%% \title{Detecting Epoch of Reionization in redshifted 21~cm: contamination in EoR window}
%% \title{Limits on the detection of the Epoch of Reionization from MWA observations of the redshifted 21~cm line}
\title{Foreground Signatures and Mitigation in Neutral Hydrogen Power Spectra From The Reionization Epoch}

>>>>

\shorttitle{Dissection of foregrounds in EoR H{\sc i} power spectra}
\shortauthors{Thyagarajan et~al.}

@@

%% \title{Detecting Epoch of Reionization in redshifted 21~cm: contamination in EoR window}
%% \title{Limits on the detection of the Epoch of Reionization from MWA observations of the redshifted 21~cm line}
\title{A Dissection of Foregrounds in Epoch of Reionization Observations from the Murchison Widefield Array}
